Bare Demo of IEEEtran.cls for Journals

### 2019-12-06 2-oracle/report/paper.tex
write template matching section

% ljy
\subsection{Template Matching}
% ljy
\subsection{Ensemble of Two Methods}

>>>>

% ljy
\subsection{Template Matching}
For the oracle bone character recognition task, we also try a traditional method, template matching, to solve it.

The principle is simple. We construct a template for each character and measure the similarity of the sample and templates. The template that has the highest similarity is believed to be the character that sample represents.

In order to construct a template, the intuition is to take all the samples of one category and take the average. However, we observe that the samples of the same character may have different size and position in the box. So the template generated by the above procedure may be blur and unrepresentative. Therefore, we preprocess the samples to find the best focus and scale. First find the center of mass of the box, which is analogous to the same term in physics. We denote the gray scale image as $G$. Consider the blackness as a measure of intensity, so we take the complement image of $G$, denoted as $\hat{G}$. i.e. $\hat{G}(i,j)=255-G(i,j)$. Then we can calculate the center of mass by the following formula:
\begin{align*}
	c_x=\frac{\sum_{i,j}\hat{G}(i,j)\cdot i}{\sum_{i,j} \hat{G}(i,j)}\\
	c_y=\frac{\sum_{i,j}\hat{G}(i,j)\cdot j}{\sum_{i,j} \hat{G}(i,j)}
\end{align*}

To determine the scale, we first set a standard scale for all the templates, say $(M,N)$. Then we search the scaling coefficient $k$ for each sample such that the new box with size $(kM,kN)$ can enclose $\sigma$ of the mass of the original box, where $\sigma\in (0,1)$ is the scaling threshold. When we increase $k$ the new box may exceed the boundary of the original box, so we add padding of all zeros (which represents white in our complement image) to thoses areas. Then we resize the new box to the standard template size. We denote the transformed sample image as $G'$. Average over such new boxes of the samples and the get the templates.

To measure the similarity of a sample and a template, we think of two metrics, normed mean square error and normed correlation, which is defined below:
\begin{align*}
	\text{NMSE}(G',T)= \frac{\sum_{x,y} (T(x,y)-G'(x,y))^2}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}\\
	\text{NCOR}(G',T)= \frac{\sum_{x,y} (T(x,y) \cdot G'(x,y))}{\sqrt{\sum_{x,y}T(x,y)^2 \cdot \sum_{x,y} G'(x,y)^2}}
\end{align*}

To compare this method with the above convolutional neural network, we do the same train-validation split.

% ljy
\subsection{Ensemble of Two Methods}
